Hyperopt-Sklearn: Automatic Hyperparameter Configuration for Scikit-Learn

### 2014-04-26 papers/2014-automl/paper.tex
paper submit

\title[Hyperopt-Sklearn]{Hyperopt-Sklearn: Subtitle?}

@@

\begin{figure}
    \centering
    \includegraphics[width=5.00in]{graphics/AverageTestScoresClassifiersTPE}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}

@@

\begin{figure}
    \centering
    \caption{
    }
    \label{fig:errtpe}
\end{figure}

@@

We have shown here that Hyperopt's random search, annealing search, and TPE algorithms make Hyperopt-sklearn viable, but the slow convergence in e.g. Figure~\ref{fig:errtpe} suggests
that other optimization algorithms might be more call-efficient.
The development of Bayesian optimization algorithms is an active research area, and  we look forward to looking at how other search algorithms interact with hyperopt-sklearn's search spaces.

@@

>>>>

\title[Hyperopt-Sklearn]{Hyperopt-Sklearn: Automatic Hyperparameter Configuration for Scikit-Learn}

@@

\begin{figure}
    \centering
    \includegraphics[width=4.50in]{graphics/AverageTestScoresClassifiersTPE}
    \caption{
        For each data set, searching the full configuration space (``Any Classifier'') delivered performance approximately on par with a search that was restricted to the best classifier type.
        (Best viewed in color.)
    }
    \label{fig:avg_test_scores}
%\vspace{-3em}
\end{figure}

@@

@@

We have shown here that Hyperopt's random search, annealing search, and TPE algorithms make Hyperopt-sklearn viable, but the slow convergence in e.g. Figure~\ref{fig:per_clf} suggests
that other optimization algorithms might be more call-efficient.
The development of Bayesian optimization algorithms is an active research area, and  we look forward to looking at how other search algorithms interact with hyperopt-sklearn's search spaces.

@@

We have introduced Hyperopt-sklearn, a Python package for automatic algorithm configuration of standard machine learning algorithms provided by Scikit-Learn.
Hyperopt-sklearn provides a unified view of 6 possible preprocessing modules and 6 possible classifiers, yet with the help of Hyperopt's optimization functions
it is able to both rival and surpass human experts in algorithm configuration.
We hope that it provides practitioners with a useful tool for the development of machine learning systems,
and automatic machine learning researchers with benchmarks for future work in algorithm configuration.
